Last glacial cycle glacier erosion potential in the Alps

### 2021-05-25 articles/erosion/response-referee1.md

In several instances we replaced "yet" with "but" and "however".

## Figures

> Fig. 2 Please indicate the outline of the connected ice stream network during
> the LGM (like in Fig. 4 of Seguinot et al., 2018). Especially in the eastern
> and SW Alps coverage largely deviates from what has been suggested from field
> data compilation (e.g. Ehlers and Gibbard, 2004). Even though outcomes might
> not be changing much, it might be helpful to know how much the %overlap is -
> erosional potential might change as fluvial topography turns into glacial one
> (e.g. Harbor, 1988) and this is probably not what you want to mix, I guess.

The field-based LGM outline was added on Fig. 2. Computing a percent overlap is
not straightforward. As for Fig. 4 in the 2018 paper, we use a manually
modified version of the Ehlers et al. (2011) data. The original data presents
numerous, expansive nunataks, many of which are found in accumulation area and
thus directly incompatible with the mass-balance scheme used in the 2018 paper.
However, the general eastward bias was discussed in two new sentences:

    It should be noted, however, that all runs presented here show a systematic
    bias with excessive glacier cover in the Eastern Alps and a diminished
    glacier extent in the Western Alps (Fig. 2a; further discussed in Seguinot
    et al., 2018). Thus the modelled patterns of erosion potential certainly
    includes a similar bias.

### 2021-05-25 articles/erosion/alps-erosion.tex
Add discussion of eastward ice cover bias.

    Different paleoclimate forcing scenarios lead to different modelled
    glaciation histories \citep[cf.][]{Seguinot.etal.2018} and thus different
    results in terms of glacial cycle cumulative erosion
    potential (Fig.~\ref{fig:sensitivity}). Scenarios including higher
    (constant, present-day) input precipitation rates yield generally higher
    modelled ice discharge and thus higher
    erosion potential (Fig.~\ref{fig:sensitivity}a--c), while scenarios
    including paleo-precipitation reductions (Fig.~\ref{fig:sensitivity}d--f),
    including our default high-resolution run
    (Fig.~\ref{fig:cumulative}), yield a smaller erosion potential. The spatial
    pattern of modelled time-integrated erosion is nevertheless generally
    consistent across the paleoclimate scenarios tested,
    despite variations in the glaciation maximum extent
    (\citealp[Fig.~3 in][]{Seguinot.etal.2018}; Fig.~\ref{fig:sensitivity}).
    Furthermore, these changes are minor
    considering the large uncertainties affecting the choice of erosion law.

>>>>

    Different paleoclimate forcing scenarios lead to different modelled
    glaciation histories \citep[cf.][]{Seguinot.etal.2018} and thus different
    results in terms of glacial cycle cumulative erosion
    potential (Fig.~\ref{fig:sensitivity}). Scenarios including higher
    (constant, present-day) input precipitation rates yield generally higher
    modelled ice discharge and thus higher
    erosion potential (Fig.~\ref{fig:sensitivity}a--c), while scenarios
    including paleo-precipitation reductions (Fig.~\ref{fig:sensitivity}d--f),
    including our default high-resolution run
    (Fig.~\ref{fig:cumulative}), yield a smaller erosion potential.

    The spatial pattern of modelled time-integrated erosion is nevertheless
    generally consistent across the paleoclimate scenarios tested,
    despite variations in the glaciation maximum extent
    (\citealp[Fig.~3 in][]{Seguinot.etal.2018}; Fig.~\ref{fig:sensitivity}).
    It should be noted, however, that all runs presented here show a systematic
    bias with excessive glacier cover in the Eastern Alps and a diminished
    glacier extent in the Western Alps (Fig.~\ref{fig:cumulative}a; further
    discussed in \citealp{Seguinot.etal.2018}). Thus the modelled patterns of
    erosion potential certainly includes a similar bias. However, uncertainties
    due to paleoclimate appear minor in regard to the much larger uncertainties
    affecting the choice of erosion law.
